---
title: "A3_JOEL_SAGMAN"
author: "Joel Sagman"
date: "1/25/2022"
output: html_document
---

## Project Info
Github Username: JoelSagman
Github Link: https://github.com/JoelSagman/Assignment-3

### Load the FallopiaData.csv
```{r setup}
library(dplyr)
FaData<-read.csv("InputData/FallopiaData.csv")
```

### Data wrangling

a. Remove rows with ‘Total’ biomass < 60
b. Reorder the columns so that they are in the order: ‘Total’, ‘Taxon’, ‘Scenario’, ‘Nutrients’, and remove the other columns
c.Make a new column TotalG, which converts the ‘Total’ column from mg to grams AND replace Total with TotalG, and add it to the dataset.

```{r data wrang}
FaData %>%
  filter(Total < 60) %>%
  relocate(Total, Taxon, Scenario, Nutrients) %>%
  select(Total:Nutrients) %>%
  mutate(TotalG = Total * 1000) # Needs to be corrected

```

### Custom Fuction
Write a custom function that will take two inputs from the user: 1. a vector of data to process (e.g. column from a data.frame object) and 2. a string that defines what calculation to perform.
1. if string #2 is "Average" then calculate the average value for the column named in vector #1 
2. if string #2 is "Sum" then calculate the sum of values for the column named in vector #1
3. if string #2 is "Observations" then count the number of observed values for the column named in vector #1
4. if string #2 is anything else, then output an error to the user 

```{r}
MyFunction<-function(FaData,var1=0,var2="string"){
  if(var2=="Average"){
    (Average=mean(var1))
  }
  if(var2=="Sum"){
    (Sum=sum(var1))
  }
  if(var2=="Observations"){
    count(var1)
  }
  if(var2 != "Average" | "Sum" | "Observations"){
    print("error not a valid input")
  }
return()
}


MyFunction(var1=FaData$Total,var2="Average")
```



## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
